Equation-of-state insensitive relations after GW170817

### 2019-02-26 paper/bin-love-after-gw170817.tex
removing one comments

\begin{abstract}
% Intro
\ky{I think some of the affiliations are messed up. For example, the MIT Kavli one (Is this Carl's?) is incomplete.}
The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical to neutron stars, yet it remains one of the largest uncertainties in nuclear physics. 
% How to probe
The extraction of tidal deformabilities from the gravitational waves emitted in the coalescence of neutron star binaries, such as GW170817, is a promising tool to probe this thermodynamic relation.
% What was done before - Binary Love
Equation-of-state insensitive relations between symmetric and antisymmetric combinations of individual tidal deformabilities, the so-called  ``binary Love relations", have proven important to infer the radius of neutron stars, and thus constrain the equation of state, from such gravitational waves. 
% What was done before - I-Love-Q
A similar set of relations between the moment of inertia, the tidal deformability, the quadrupole moment, and the compactness of neutron stars, the so-called ``I-Love-Q" and ``C-Love" relations, allow for future tests of General Relativity in the extreme gravity regime. 
% What we will do
But even the most insensitive of such relations still presents some degree of equation-of-state variability that could introduce systematic uncertainties in parameter extraction and in model selection. 
%
We here reduce this variability by more than $50\%$ by imposing a prior on the allowed set of equations of state, derived from the posteriors generated from the analysis of GW170817.  
%
The resulting increase in insensitivity reduces systematic uncertainties in the extraction of the tidal deformability from future gravitational wave observations, although statistical uncertainties currently dominate the error budget, and will continue to do so until the era of Voyager-class detectors.  
\end{abstract}

>>>>

\begin{abstract}
% Intro
The thermodynamic relation between pressure and density (i.e.~the equation of state) of cold supranuclear matter is critical to neutron stars, yet it remains one of the largest uncertainties in nuclear physics. 
% How to probe
The extraction of tidal deformabilities from the gravitational waves emitted in the coalescence of neutron star binaries, such as GW170817, is a promising tool to probe this thermodynamic relation.
% What was done before - Binary Love
Equation-of-state insensitive relations between symmetric and antisymmetric combinations of individual tidal deformabilities, the so-called  ``binary Love relations", have proven important to infer the radius of neutron stars, and thus constrain the equation of state, from such gravitational waves. 
% What was done before - I-Love-Q
A similar set of relations between the moment of inertia, the tidal deformability, the quadrupole moment, and the compactness of neutron stars, the so-called ``I-Love-Q" and ``C-Love" relations, allow for future tests of General Relativity in the extreme gravity regime. 
% What we will do
But even the most insensitive of such relations still presents some degree of equation-of-state variability that could introduce systematic uncertainties in parameter extraction and in model selection. 
%
We here reduce this variability by more than $50\%$ by imposing a prior on the allowed set of equations of state, derived from the posteriors generated from the analysis of GW170817.  
%
The resulting increase in insensitivity reduces systematic uncertainties in the extraction of the tidal deformability from future gravitational wave observations, although statistical uncertainties currently dominate the error budget, and will continue to do so until the era of Voyager-class detectors.  
\end{abstract}
